Analysis of the included studies

### 2023-06-19 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Combined the two data loading chunks

```{r}
args <- c(
  here::here("data", "review_data_long_cleaned.rds"),
  here::here("data", "review_data_compact_cleaned.rds"),
  here::here("data", "compact_data_with_citation_keys_cleaned.rds")
  )
```

```{r}
# Load the cleaned data 
long_data <- readRDS(args[1])

>>>>

```{r}
args <- c(
  here::here("data", "review_data_long_cleaned.rds"),
  here::here("data", "review_data_compact_cleaned.rds"),
  here::here("data", "compact_data_with_citation_keys_cleaned.rds")
  )

# Load the cleaned data 
long_data <- readRDS(args[1])
